%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{setspace}
\input{alias.tex}
\setlength{\parskip}{0.6em}
\usepackage{ragged2e}
\usepackage{xspace}
\usepackage{url}
\usepackage{enumitem}
\usepackage{etaremune}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{color,soul}
\usepackage{hyperref}
%\usepackage{academicons}
%\fancypagestyle{CVfooter}
\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

\pagestyle{fancy}
\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}
\lfoot{Chris Brown}
\cfoot{}
\rfoot{\thepage\ of \pageref{LastPage}
 }
\fancypagestyle{firstpage}{%
\fancyhf{} 
  \lfoot{\textbf{Dr.} \me}
  \cfoot{\textit{Last Updated:} \today} %DATE
  \rfoot{\thepage\ of \pageref{LastPage}}
}
 \renewcommand{\footrulewidth}{0.5pt}


\name{\Large{Dwayne Christian Brown, Jr. (``Chris")}\\
    \small{Assistant Professor $|$ Department of Computer Science $|$ Virginia Tech}} 
\address{
    {\email{dcbrown@vt.edu} \location{Blacksburg, VA} \homepage{https://people.cs.vt.edu/dcbrown/} %\linkedin{in/chris-brown-04840654} 
    \github{chbrown13}
    \twitter{@d\_chrisbrown2}}
} 

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-10pt}
\begin{rSection}{Education}
\thispagestyle{firstpage}
{\bf North Carolina State University} \hfill {2015 - 2021} \\ 
\textit{Ph.D.} in Computer Science \\
Dissertation: \textit{Digital Nudges for Encouraging Developer Actions} \\
Advised by Dr. Chris Parnin

% {\bf North Carolina State University} \hfill {September 2019 - present} \\
% \textit{Graduate Certificate} in Teaching and Communication \\
% The Graduate School Professional Development

{\bf North Carolina State University} \hfill {2015 - 2017} \\ 
\textit{M.S.} in Computer Science

{\bf Duke University} \hfill {2009 - 2013} \\ 
\textit{B.S.} in Computer Science, with Distinction \\
Minor in African and African American Studies

\underline{\textsc{Additional Education}}\vspace{2.5pt}\\ 
\begin{rSubsection}{North Carolina State University}{2019 - 2021}{Teaching and Communication Graduate Certificate}{}
\end{rSubsection}

\end{rSection}
% \vspace{-5pt}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Employment History}

\begin{rSubsection}{Virginia Polytechnic Institute and State University (Virginia Tech)}{Blacksburg, VA}{Assistant Professor, Fall 2021 - present}{}
\end{rSubsection}

\begin{rSubsection}{North Carolina State University (NC State)}{Raleigh, NC}{Research Assistant, Fall 2016 - Spring 2021\newline Teaching Assistant, Fall 2015 - Spring 2016}{}
\end{rSubsection}

\begin{rSubsection}{Red Hat}{Raleigh, NC}{Quality Engineering Intern, Summers 2017 and 2018}{}
\end{rSubsection}
%\vspace{-5pt}

\begin{rSubsection}{Blackbaud}{Charleston, SC}{Software Quality Engineer Intern, Summer 2016}{}
\end{rSubsection}
%\vspace{-5pt}

\begin{rSubsection}{Bank of America}{Charlotte, NC}{Python Developer, July 2013 - July 2015}{}
\end{rSubsection}

\end{rSection}
%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications}
\textit{My name is in bold, underlined names are students directly supervised by me. A publication list is also available on \href{https://scholar.google.com/citations?hl=en\&user=MmgiKNkAAAAJ\&view_op=list_works\&authuser=1\&gmla=AJsN-F78_HJ89LDIopy2rAQwWOkF_D8aDZ4dGsFilA7BpNCva8nj8QOzFJG1H_1kyk0-EYHSBgHrKWtEx9OmEsMZNOix11gDuFgjgbvfCIE_xP_whZAtBW8}{Google Scholar}.} %  


%------------------------------------------------
\textbf{Journal Publications}

\begin{enumerate}[{start=3,label=[J\arabic*]\addtocounter{enumi}{-2}}]
    \item Kashumi Madampe and John Grundy and Judith Good and Dulaji Hidellaarachchi and J\'{a}come Cunha and \me and Peng Kuang and Reham Al Tamime and Ariful Islam Anik and Advait Sarkar and Wei Zhou and \underline{Shawal Khalid} and Tommaso Turchi and Shavindra Wickramathilaka and Yue Jiang. \textit{Addressing the Agony of Recruitment for Human-centric Computing Studies}. ACM Special Interest Group on Software Engineering (SIGSOFT) Software Engineering Notes. \url{https://doi.org/10.1145/3721890.3721898}
    \item Sonja Hyrynnerlmi, Sebastian Baltes, \me, Rafael Prikladnicki, Gema Rodríguez-Pérez, Jocelyn Simmonds, Bianca Trinkenreich, Yi Wang, and Grischa Liebel. \textit{Making Software Development More Diverse and Inclusive: Key Themes, Challenges, and Future Directions}. ACM Transactions on Software Engineering and Methodology (TOSEM), Special Issue: ``A 2030 Roadmap for Software Engineering''. [\url{https://doi.org/10.1145/3711904}]
    \item Peipei Wang, \me, Jamie A. Jennings, Kathryn T. Stolee. \textit{Demystifying Regular Expression Bugs: A comprehensive study on regular expression bug causes, fixes, and testing}. Empirical Software Engineering (EMSE 2022). [\url{https://doi.org/10.1007/s10664-021-10033-1}]
\end{enumerate}

%------------------------------------------------
\textbf{Conference Publications}

\begin{enumerate}[{start=35,label=[C\arabic*]\addtocounter{enumi}{-2}}]
    \item  Taufiq Daryanto, Sophia Stil, Xiaohan Ding, Daniel Manesh, Sang Won Lee, Tim Lee, Stephanie Lunn, Sarah Rodriguez, \me and Eugenia Rho. \textit{Designing Conversational AI to Support Think-Aloud Practice in Technical Interview Preparation for CS Students}. IEEE Symposium on Visual Languages and Human-Centric Computing (VL/HCC 2025). [31\% acceptance rate].
    \item \underline{Minhyuk Ko}, \ul{Omer Ahmed}, \ul{Yoseph Berhanu Alebachew}, \me. \textit{AutoPrint: Judging the Effectiveness of An Automatic Print Statement Debugging Tool}. IEEE Symposium on Visual Languages and Human-Centric Computing (VL/HCC 2025). [\textit{short paper}, 37\% acceptance rate]
    \item \underline{Huayu Liang}, \ul{Syeda Afia Hossain}, and \me. \textit{Understanding User and Developer Perceptions of and Responses to Dark Patterns in Online UIs}. IEEE Symposium on Visual Languages and Human-Centric Computing (VL/HCC 2025). [\textit{short paper}, 37\% acceptance rate]
    \item \underline{Minhyuk Ko}, Mohammed Seyam, and \me. \textit{Programmers Without Borders: Bridging Cultures in Computer Science Study Abroad Program}. IEEE Symposium on Visual Languages and Human-Centric Computing (VL/HCC 2025). [\textit{short paper}, 37\% acceptance rate]
    \item \me, \underline{Jason Cusati}. \textit{Exploring the Evidence-Based SE Beliefs of Generative AI Tools}. ACM/IEEE International Symposium on Empirical Software Engineering and Measurement (ESEM) Emerging Results and Vision track. [30\% acceptance rate]
    \item \underline{Xiaoxiao Gan}, \me. \textit{Exploring the Impact of Integrating UI Testing in CI/CD Workflows on GitHub}. International Conference on Mining Software Repositories (MSR) Registered Report track. \url{https://arxiv.org/pdf/2504.19335}
    \item \underline{Tianjia Wang}, \underline{Matthew Trimble}, \me. \textit{DevCoach: Supporting Students Learning the Software Development Life Cycle with a Generative AI powered Multi-Agent System}. Foundations of Software Engineering Software Engineering Education Track (FSE SEET 2025). [37\% acceptance rate] \url{https://doi.org/10.1145/3696630.3727255}
    \item \underline{Brian Bell}, Teresa Thomas, Sang Won Lee, \me. \textit{How do Software Engineering Candidates Prepare for Technical Interviews?}. Foundations of Software Engineering Software Engineering Education Track (FSE SEET 2025). [37\% acceptance rate] \url{https://doi.org/10.1145/3696630.3727245}
    \item \underline{Yoseph Berhanu Alebachew}, \underline{Minhyuk Ko}, \me. \textit{Are We on the Same Page? Examining Developer Perception Alignment in Open Source Code Reviews}. International Conference on Evaluation and Assessment in Software Engineering (EASE 2025). [27\% acceptance rate]
    \item  \underline{Dibyendu Brinto Bose}, \underline{Travis Chan}, \underline{Matthew Trimble}, \me. ``\textit{AutoPyDep: A Recommendation System for Python Dependency Management Utilizing Graph-Based Analytics}''. Foundations of Software Engineering (FSE 2025) Tool Demonstration track. \url{https://doi.org/10.1145/3696630.3728576}
    \item \underline{Swanand Vaishampayan}, \underline{Hunter Leary}, \underline{Yoseph Berhanu Alebachew}, Louis Hickman, Brent Stevenor, Fletcher Wimbush, Weston Beck, \me. \textit{Human and LLM-Based Resume Matching: An Observational Study}. Annual Conference of the Nations of the Americas Chapter of the Association for Computational Linguistics (NAACL 2025). [15\% acceptance rate] \url{https://aclanthology.org/2025.findings-naacl.270/}
    \item \underline{Swanand Vaishampayan}, \me. \textit{Will You Trust Me More Than ChatGPT? Evaluating LLM-Generated Code Feedback for Mock Technical Interviews}. International Conference on Cooperative and Human Aspects of Software Engineering (CHASE 2025). [27\% acceptance rate] \url{https://doi.org/10.1109/CHASE66643.2025.00018}
    \item \underline{Xiaoxiao Gan}, \underline{Huayu Liang}, \me. \textit{Challenges, Strategies, and Impacts: A Qualitative Study on UI Testing in CI/CD Processes from GitHub Developers’ Perspectives}. International Conference on Software Testing, Verification and Validation (ICST 2025). \url{https://doi.org/10.1109/ICST62969.2025.10988972}
    \item Ebtesam Al Haque, \me, Thomas D. LaToza, Brittany Johnson. \textit{Towards Decoding Developer Cognition in the Age of AI Assistants}. IEEE International Conference on Software Analysis, Evolution and Reengineering (SANER 2025) Registered Report track. \url{https://arxiv.org/pdf/2501.02684}
    \item \underline{Swanand Vaishampayan}, Muhammad Ali Gulzar, \me. \textit{Improving Evidence-Based Tech Hiring with GitHub-Supported Resume Matching}. IEEE International Conference on Software Analysis, Evolution and Reengineering (SANER 2025). [23\% acceptance rate] \url{https://doi.org/10.1109/SANER64311.2025.00081}
    
    \item \underline{Tianjia Wang}, Tong Wu, Huayi Li, \me, Yan Chen. \textit{Generative Co-Learners: Enhancing Cognitive and Social Presence of Students in Asynchronous Learning with Generative AI}. ACM International Conference on Supporting Group Work (GROUP 2024). \url{https://doi.org/10.1145/3701198}
    
    \item \underline{Lucas Franke}, \underline{Huayu Liang}, \underline{Sahar Farzanehpour}, Aaron Brantly, James C. Davis, \me. \textit{An Exploratory Mixed-methods Study on General Data Protection Regulation (GDPR) Compliance in Open-Source Software}. International Symposium on Empirical Software Engineering and Measurement. (ESEM 2024) [20\% acceptance rate] \url{https://doi.org/10.1145/3674805.3686692}
    
    \item \underline{Arpit Thool}, \me. \textit{Harnessing the Power of LLMs to Simplify Security: LLM Summarization for Human-Centric DAST Reports}. Visual Languages and Human-Centric Computing (VL/HCC 2024). [\textit{short paper}] \url{https://doi.org/10.1109/VL/HCC60511.2024.00014}

    \item \underline{Shawal Khalid}, \underline{Huayu Liang}, \me. \textit{Exploring User Perceptions of Crypto Signals: An Empirical Study From Social Media Posts}. International Conference on Blockchain (Blockchain 2024). \url{10.1109/Blockchain62396.2024.00071}
    
    \item \underline{Tianjia Wang}, Ramaraja Ramanujan, Yi Lu, Chenyu Mao, Yan Chen, \me. \textit{DevCoach: Supporting Students in Learning the Software Development Life Cycle at Scale with Generative Agents}. Learning at Scale, Work in Progress (L@S WIP 2024). [\textit{short paper}] \url{https://dl.acm.org/doi/10.1145/3657604.3664663}
    
    \item \underline{Sean Gruber}, \underline{Grace Govan}, \me. \textit{Exploring Disparities in Student and Practitioner Perceptions of Skill Proficiency with SE Gap Awareness}. Learning at Scale, Work in Progress (L@S WIP 2024). [\textit{short paper}] \url{https://doi.org/10.1145/3657604.3664684}
    
    \item \underline{Dibyendu Brinto Bose}, Brendan David-John, \me. \textit{Optimizing AR Application Testing: Integrating Metamorphic Testing to Address Developer and End-User Challenges}. International Conference on Human-Computer Interaction (HCI International 2024) Late Breaking Work [\textit{extended abstract}] \url{https://doi.org/10.1007/978-3-031-76812-5_2}
    
    \item Sabaat Haroon, \me, Muhammad Ali Gulzar. \textit{DeSQL: Interactive Debugging of SQL in Data-Intensive Scalable Computing}. ACM International Conference on the Foundations of Software Engineering (FSE 2024). \url{https://doi.org/10.1145/3643761}
        
    \item \underline{Shawal Khalid}, \me. \textit{Software Engineering Approaches Adopted by Blockchain Developers}. International Workshop on Blockchain Applications and Theory (BAT 2023). \url{https://doi.org/10.1109/SDS59856.2023.10329007}
    
    \item \underline{Tianjia Wang}, Daniel Vargas Diaz, \me, Yan Chen. \textit{Towards Adapting Computer Science Courses to AI Assistants' Capabilities}. Visual Languages and Human-Centric Computing (VL/HCC 2023). [29\% acceptance rate] \url{https://doi.org/10.1109/VL-HCC57772.2023.00018}
    
    \item \underline{Minhyuk Ko}, \underline{Dibyendu Brinto Bose}, Hemayet Ahmed Chowdhury, Mohammed Seyam, \me. \textit{Exploring the Barriers and Factors that Influence Debugger Usage for Students}. Visual Languages and Human-Centric Computing (VL/HCC 2023). [\textit{short paper}, 29\% acceptance rate] \url{https://doi.org/10.1109/VL-HCC57772.2023.00027} \\ \textbf{\texttt{\hl{\faTrophy~Best Short Paper, Honorable Mention~\faTrophy}}}

    \item \underline{Swanand Vaishampayan}, \underline{Sahar Farzanehpour}, \me. \textit{Procedural Justice and Fairness in Automated Resume Parsers for Tech Hiring: Insights from Candidate Perspectives}. Visual Languages and Human-Centric Computing (VL/HCC 2023). [\textit{short paper}, 29\% acceptance rate] \url{https://doi.org/10.1109/VL-HCC57772.2023.00019}

    \item Mahnaz Behroozi, Chris Parnin, \me. \textit{Asynchronous Technical Interviews: Reducing the Effect of Supervised Think-Aloud on Communication Ability}. Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering (ESEC/FSE 2022). [22\% acceptance] \url{https://doi.org/10.1145/3540250.3549168} \\ \textbf{\texttt{\hl{\faTrophy~Distinguished Paper Award~\faTrophy}}}

    \item \me, Chris Parnin. \textit{Comparing Different Developer Behavior Recommendation Styles}. International Conference on Cooperative and Human Aspects of Software Engineering (CHASE 2021). \url{https://doi.org/10.1145/3387940.3391481}
    
    
    \item \me, Chris Parnin. \textit{Understanding the Impact of GitHub Suggested Changes on Recommendations Between Developers}. Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering (ESEC/FSE 2020). \url{https://doi.org/10.1145/3368089.3409722}
    
    \item Peipei Wang, \me, Jamie A. Jennings, Kathryn T. Stolee. \textit{An Empirical Study on Regular Expression Bugs}. International Conference on Mining Software Repositories (MSR 2020). \url{https://doi.org/10.1145/3379597.3387464}
    
    \item Peng Sun, \me, Ivan Beschastnikh, Kathryn T. Stolee. \textit{Mining Specifications from Documentation Using a Crowd}. International Conference on Software Analysis, Evolution and Reengineering (SANER 2019). \url{https://doi.org/10.1109/SANER.2019.8668025}
    
    \item \me, Justin Middleton, Esha Sharma, Emerson Murphy-Hill. \textit{How Software Users Recommend Tools to Each Other}. Visual Languages and Human-Centric Computing (VL/HCC 2017). \url{https://doi.org/10.1109/VLHCC.2017.8103460}
        
    \item Justin Smith, \me, Emerson Murphy-Hill. \textit{Flower: Navigating Program Flow in the IDE}. Visual Languages and Human-Centric Computing (VL/HCC 2017). \url{https://doi.org/10.1109/VLHCC.2017.8103445}
    
    \item Susan H. Rodger, \textbf{Dwayne Brown}, Michael Hoyle, Daniel MacDonald, Michael Marion, Elizabeth Onstwedder, Bella Onwumbiko, Edwin Ward. \textit{Weaving Computing into all Middle School Disciplines}. Innovation and Technology in Computer Science Education (ITiCSE 2014). \url{https://doi.org/10.1145/2591708.2591754}
\end{enumerate}

%------------------------------------------------
\textbf{Workshop Publications}

\begin{enumerate}[{start=24,label=[W\arabic*]\addtocounter{enumi}{-2}}]
\item \underline{Dibyendu Brinto Bose}, \underline{Yoseph Alebachew Berhanu}, and \me. \textit{LLMs in Debate: Does Arguing Make Them Better at Detecting Metamorphic Relations?}. International Workshop on Autonomous Agents in Software Engineering (AgenticSE 2025).
    \item \underline{Ryan Wood}, \me. \textit{Understanding User Perceptions of Automated Dark Pattern Detection Online}. Designing for Everyone: Advancing User Experience Through Human-Centric Design Methodologies.
    \item \underline{Swanand Vaishampayan}, \me. \textit{Do LLM-Generated Resumes Make Me More Qualified? An Observational Study of LLMs For Resume Generation and Matching Tasks}. Designing for Everyone: Advancing User Experience Through Human-Centric Design Methodologies.
    \item \underline{Minhyuk Ko}, \underline{Shawal Khalid}, \me. \textit{ParticipantGuide: Promoting Transparency in Human-Centric User Studies}. Designing for Everyone: Advancing User Experience Through Human-Centric Design Methodologies.
    \item \underline{Shawal Khalid}, \me. \textit{Evaluating Capabilities and Perspectives of Generative AI Tools in Smart Contract Development}.  International Symposium on Blockchain and Secure Critical Infrastructure (BSCI).
    \item Ebtesam Al Haque, \me, Thomas D. LaToza, Brittany Johnson. \textit{The Evolution of Information Seeking in Software Development: Understanding the Role and Impact of AI Assistants}. Workshop on Human-Centered AI for SE (HumanAISE). \url{https://doi.org/10.1145/3696630.3731665}
    \item \me, \underline{Swanand Vaishampayan}. \textit{Towards Evidence-Based Tech Hiring Pipelines}. Software Engineering in 2030 Workshop (SE2030). \url{https://arxiv.org/abs/2504.06387}
    \item \underline{Dibyendu Brinto Bose}. \textit{From Prompts to Properties: Rethinking LLM Code Generation with Property-Based Testing}. International Workshop on Large Language Model-Oriented Empirical Research (LLANMER 2025). \url{https://doi.org/10.1145/3696630.3728702}
    \item \underline{Sahar Farzanepour}, \underline{Swetha Rajeev}, \underline{Huayu Liang}, Ritvik Prabhu, and \me. \textit{ResearchBot: Bridging the Gap Between Academic Research and Practical Programming Communities}. International Workshop on Bots in Software Engineering (BotSE 2025). \url{https://doi.org/10.1109/BotSE67031.2025.00017}
    \item \underline{Shawal Khalid}, \underline{Huayu Liang}, \me. \textit{Decoding the Influence: Analyzing the Impact of Crypto Signals on Software Repositories}. International Workshop on Blockchain Oriented  Software Engineering (IWBOSE 2025).
    \item \underline{Dibyendu Brinto Bose}, \me. \textit{An Empirical Study on Current Practices and Challenges of Core AR/VR Developers}. International Workshop on Virtual and Augmented Reality Software Engineering (VARSE 2024). \url{https://doi.org/10.1145/3691621.3694956}
    \item \underline{Shawal Khalid}, \me. \textit{Exploring Stakeholder Challenges in Recruitment for Human-Centric Computing Research}. Workshop on Addressing Challenges in Recruiting Participants for Human-Centric Computing Research Studies (VL/HCC Workshop 2024). \url{https://doi.org/10.1109/VL/HCC60511.2024.00068}
    \item \underline{Yoseph Berhanu Alebachew}, \me. \textit{Proposed Experiment on Automatic Bias Detection in Source Code Review}. Annual Workshop of the Psychology of Programming Interest Group (PPIG 2024). \url{https://www.ppig.org/files/2024-PPIG-35th-alebachew.pdf}
    \item Sonja Hyrynsalmi, Sebastian Baltes, \me, Rafael Prikladnicki, Gema Rodríguez-Pérez, Jocelyn Simmonds, Bianca Trinkenreich, Yi Wang, and Grischa Liebel. \textit{Bridging Gaps, Building Futures: Advancing Software Developer Diversity and Inclusion Through Future-Oriented Research}. Software Engineering in 2030 Workshop (SE2030). \url{https://arxiv.org/abs/2404.07142v1}
    \item \underline{Arpit Thool}, \me. \textit{Securing Agile: Assessing the Impact of Security Activities on Agile Development}. International Workshop on Secure Software: Challenges, Opportunities, and Lessons Learned co-located with the International Conference on Evaluation and Assessment in Software Engineering (Secure Software 2024). \url{https://dl.acm.org/doi/10.1145/3661167.3661280}
    \item  \underline{Shawal Khalid}, \me. \textit{Software Engineering Approaches Adopted By Blockchain Developers}. International Workshop on Blockchain Applications and Theory in conjunction with the International Conference on Software Defined Systems (BAT 2023). \url{https://doi.org/10.1109/SDS59856.2023.10329007}
    \item  \underline{Nivishree Palvannan}, \me. \textit{Suggestion Bot: Analyzing the Impact of Automated Suggested Changes on Code Reviews}. International Workshop on Bots in Software Engineering in conjunction with the International Conference on Software Engineering (BotSE 2023). \url{https://doi.org/10.1109/BotSE59190.2023.00015}
     
    \item  \underline{Md Mahim Anjum Haque}, Wasi Uddin Ahmad, Ismini Lourentzou, \me.
     \textit{FixEval: Execution-based Evaluation of Program Fixes for Programming Problems}. International Workshop on Automated Program Repair in conjunction with the International Conference on Software Engineering (APR 2023). %[\url{https://program-repair.org/workshop-2023/}]

    \item \me. \textit{Nudging Developers to Participate in SE Research}. International Workshop on Recruitment Of Participants for Empirical SE Studies in conjunction with the International Conference on Software Engineering (ROPES 2022). \url{https://ropes-workshops.github.io/ropes22/}
    
    \item \me, Chris Parnin. \textit{Dark Patterns for Influencing Developer Behavior}. What Can CHI Do About Dark Patterns? Workshop in conjunction with the ACM Conference on Human Factors in Computing Systems  (Dark Patterns 2021). \url{https://darkpatternsindesign.com/position-papers/}
    
    \item \me, Chris Parnin. \textit{Nudging Students Toward Better Software Engineering Behaviors}. International Workshop on Bots in Software Engineering in conjunction with the International Conference on Software Engineering (BotSE 2021). \url{https://doi.org/10.1109/BotSE52550.2021.00010}
    
    \item \me, Chris Parnin. \textit{Sorry to Bother You Again: Developer Recommendation Choice Architectures for Designing Effective Bots}. International Workshop on Bots in Software Engineering in conjunction with the International Conference on Software Engineering (BotSE 2020). \url{https://doi.org/10.1145/3387940.3391506}
    
    \item \me, Chris Parnin. \textit{Sorry to Bother You: Designing Bots for Effective Recommendations}. International Workshop on Bots in Software Engineering in conjunction with the International Conference on Software Engineering (BotSE 2019). \url{https://doi.org/10.1109/BotSE.2019.00021}
        
    \item Susan H. Rodger, Steve Cooper, Wanda Dann, \textbf{Dwayne C. Brown}, Jacobo Carrasquel. \textit{Experimenting with and Integrating Alice 2.3 into many disciplines (abstract only)}. Special Interest Group on Computer Science Education (SIGCSE 2013). \url{https://doi.org/10.1145/2445196.2445513}
\end{enumerate}

%------------------------------------------------

%------------------------------------------------
\textbf{Lightning Talks and Posters}

\begin{enumerate}[{start=5,label=[P\arabic*]\addtocounter{enumi}{-2}}]
    \item \underline{Tianjia Wang}, \me. ``Aligning Software Engineering Education with Generative AI:
  Insights from Developers, Instructors with Concept Inventory Design''. \textit{International Computing Education Research} (ICER 2025). [lightning talk]
  \item \underline{Xiaoxiao Gan}, \me. ``Designing a Comprehensive and Practical Testing Curriculum for
  Undergraduate Computer Science Students''. \textit{International Computing Education Research} (ICER 2025). [lightning talk]
    \item \underline{Minhyuk Ko}, \underline{Dibyendu Brinto Bose}, Weiu Wang, Mohammed Seyam, \me. ``Understanding the Performance of Large Language Model to Generate SQL Queries''. \textit{Visual Languages and Human-Centric Computing Posters and Showpieces track} (VL/HCC 2024). \url{https://doi.org/10.1109/VL/HCC60511.2024.00048}
    \item \underline{Lucas Franke}, \underline{Huayu Liang}, Aaron Brantly, James C. Davis, \me. ``A First Look at the General Data Protection Regulation (GDPR) in Open-Source Software''. \textit{International Conference on Software Engineering, Posters track} (ICSE 2024). \url{https://doi.org/10.1145/3639478.3643077}
    \item Susan H. Rodger, \textbf{Dwayne C. Brown}, Michael Hoyle, Michael Marion. ``Integrating Computer Science into Middle School Mathematics''. \textit{Special Interest Group on Computer Science Education} (SIGCSE 2013). [poster] \url{https://doi.org/10.1145/2445196.2445424}
\end{enumerate}

\textbf{Doctoral Symposia}

\begin{enumerate}[{start=5,label=[DS\arabic*]\addtocounter{enumi}{-2}}]
    \item \underline{Yoseph Alebachew Berhanu}. ``AI-Guided Exploration of Large-Scale Codebases''. \textit{Visual Languages and Human-Centric Computing Graduate Consortium} (VL/HCC GC 2025).
    \item \underline{Minhyuk Ko}. ``Autoprint: An Automatic Print Statement Insertion Tool''. \textit{Richard Tapia Celebration of Diversity in Computing Conference Doctoral Consortium} (Tapia 2024).
    \item \underline{Shawal Khalid}. ``A Comprehensive Approach to Supporting Blockchain Developers''. \textit{Visual Languages and Human-Centric Computing Graduate Consortium} (VL/HCC GC 2024).
    \item \underline{Swanand Vaishampayan}. ``Procedural Justice for Computer Science Hiring: Towards Fair and Equitable AI''. \textit{Visual Languages and Human-Centric Computing Graduate Consortium} (VL/HCC GC 2024).
    \item \me. ``Nudges for Encouraging Developer Actions''. \textit{International Conference on Software Engineering: Companion Proceedings} (ICSE 2019). \url{https://doi.org/10.1109/ICSE-Companion.2019.00082}
\end{enumerate}

\textbf{Undergraduate Research Posters}
\begin{enumerate}[{start=12,label=[P\arabic*]\addtocounter{enumi}{-2}}]
    \item \underline{Javier Ralat}. ``Ask A Researcher: Transforming Research to Practice.'' \textit{Virginia Tech Summer Research Symposium}. Virginia Tech Multicultural Academics Opportunities Program (MAOP 2024).
    \item \underline{Syeda Hossain}. ``
    Understanding User and Developer Perceptions of Dark Patterns in Software.'' \textit{Virginia Tech Summer Research Symposium}. Virginia Tech Multicultural Academics Opportunities Program (MAOP 2024).
    \item \underline{Travis Chan}. ``User Interface Development using CustomTkinter for Automating Python Dependency Recognition.'' \textit{Virginia Tech Summer Research Symposium}. Virginia Tech Multicultural Academics Opportunities Program (MAOP 2024).
    \item \underline{Yasemin Tanyu}, \underline{Peiqing Guo}, \me. ``Modernizing the Academic Journey: A User-Centric Plan of Study Tool for MS and PhD Students in CS''. \textit{Virginia Tech Undergraduate Research in Computer Science Spring Symposium} (VTURCS 2024). \textbf{\texttt{\hl{\faTrophy~2nd Place, Research Division~\faTrophy}}}
    \item \underline{Matthew Trimble}, \underline{Dibyendu Brinto Bose}, \me. ``Python Library Release Predictions''. \textit{Virginia Tech Undergraduate Research in Computer Science Spring Symposium} (VTURCS 2024). \textit{Virginia Tech Undergraduate Research in Computer Science Spring Symposium} (VTURCS 2024).
    \item \underline{Omer Ahmed}, \me. ``AI Tools vs Debugging Tools: Exploring User Perceptions on Bug Locating Performance''. \textit{Virginia Tech Summer Research Symposium}. Virginia Tech Multicultural Academics Opportunities Program (MAOP 2023).
    \item \underline{Edwin Lewis II}, \me. ``Postmortems: The Game Development Process''. \textit{Virginia Tech Summer Research Symposium}. Virginia Tech Multicultural Academics Opportunities Program (MAOP 2023).
    \item \underline{Colin Roberts}, \me. ``Enhancing Debugging Efficiency: User Perspectives on AutoPrint, an Automated Print Statement Tool''. \textit{Virginia Tech Summer Research Symposium}. Virginia Tech Multicultural Academics Opportunities Program (MAOP 2023). [poster]
    \item \underline{Sahar Farzanehpour}, \me, \underline{Swanand Vaishampayan}. ``Automated Resume Parsing: Resume vs. Online Profiles''. \textit{Virginia Tech Undergraduate Research in Computer Science Spring Symposium} (VTURCS 2023).
    \item \underline{Jenna Krebs}, \me. ``A Study of Exponent and Pramp as Technical Interview Preparation Tools''. \textit{Dennis Dean Undergraduate Research and Creative Scholarship Conference}. Virginia Tech, 2023.
    \item Hennah Nazari, \underline{Brian Bell}, \textbf{Chris Brown}, Sang Won Lee. ``Understanding Challenges in Technical-Interview Preparation Process''. \textit{Virginia Tech Undergraduate Research in Computer Science Spring Symposium} (VTURCS 2022). 
    \item \underline{Grace Govan}, \underline{Sean Gruber}, \textbf{Chris Brown}. ``Gaps in Software Engineering Education''. \textit{Virginia Tech Undergraduate Research in Computer Science Spring Symposium} (VTURCS 2022). 
\end{enumerate}

\textbf{Other Non-Published Symposia, Conferences, Workshops, and Posters}    
\begin{enumerate}[{start=14,label=[O\arabic*]\addtocounter{enumi}{-2}}]
    \item \underline{Swanand Vaishampayan}, \me. ``Human and LLM-Based Resume Matching: An Observational Study''. \textit{Amazon-Virginia Tech Initiative for Efficient and Robust Machine Learning}. 2024. [poster]
    \item \underline{Dibyendu Brinto Bose}, \underline{Travis Chan}, \underline{Matthew Trimble}, \me. ``AutoPyDep: A Recommendation System for Python Dependency Management Utilizing Graph-Based Analytics''. \textit{Amazon-Virginia Tech Initiative for Efficient and Robust Machine Learning}. 2024. [poster]
    \item \underline{Omer Ahmed}. ``AI Tools vs Debugging Tools: Exploring User Perceptions on Bug Locating Performance''. \textit{VA–NC Alliance Undergraduate Research Symposium}. 2024. Louis Stokes Alliances for Minority Participation (LSAMP) Program, Charlottesville, VA. \textbf{\texttt{\hl{\faTrophy~1st Place~\faTrophy}}}
    \item \underline{Omer Ahmed}. ``AI Tools vs Debugging Tools: Exploring User Perceptions on Bug Locating Performance''. \textit{Virginia State University Annual Research Conference}. 2024. Virginia State, Petersburg, VA.
    \item \underline{Shawal Khalid}. ``Unveiling the Potential of Blockchain in Software Engineering and HCI: An Exploratory Reflection''. \textit{CHCI Big Ideas Workshop}. Center for Human-Computer Interaction, Virginia Tech, 2024. [lightning talk]
    \item \underline{Shawal Khalid}, \me. ``Smart Contract Generation: A Comparison Between Generative AI Tools''. \textit{ACM Capital Region Celebration of Women in Computing} (CAPWIC 2024). Charlottesville, VA.
    \item \underline{Huayu Liang}, \me. ``Understanding End User and Software Engineer Perceptions of Dark Patterns''. \textit{ACM Capital Region Celebration of Women in Computing} (CAPWIC 2024). Charlottesville, VA.
    \item \underline{Xiaoxiao Gan}, \me. ``Exploring Challenges of Integrating GUI Testing Framework in CI/CD Workflows on Open Source Repositories''. \textit{ACM Capital Region Celebration of Women in Computing} (CAPWIC 2024). Charlottesville, VA. [poster]
    \item \underline{Minhyuk Ko}. ``AutoPrint: Automatic Print Statement Insertion Tool''. \textit{Eastern Atlantic Students in Software Engineering Colloquium} (ESSEC 2024). William \& Mary, Williamsburg, VA.
    \item \underline{Shawal Khalid}. ``Smart Contract Generation: Comparison Between Generative AI Tools''. \textit{Eastern Atlantic Students in Software Engineering Colloquium} (ESSEC 2024). William \& Mary, Williamsburg, VA.
    \item \underline{Xiaoxiao Gan}. ``Exploring Challenges of Integrating GUI Testing framework in CI/CD Workflows on Open Source Repositories''. \textit{Eastern Atlantic Students in Software Engineering Colloquium} (ESSEC 2024). William \& Mary, Williamsburg, VA.
    \item \underline{Omer Ahmed}, \me. ``AI Tools vs Debugging Tools: Exploring User Perceptions on Bug Locating Performance''. \textit{Dr. Wayne Scales Undergraduate Research and Creative Scholarship Symposium}. Virginia Tech, 2024. \textbf{\texttt{\hl{\faTrophy~2nd Place~\faTrophy}}}
    \item \underline{Minhyuk Ko}. ``Automatic Print Statement Insertion Tool''. \textit{CHCI Big Ideas Workshop}. Center for Human-Computer Interaction, Virginia Tech, 2023. [lightning talk]
    \item \me. ``Repurposing Software Engineering Faux Pas to Improve Developer Behavior''. \textit{CHCI Big Ideas Workshop}. Center for Human-Computer Interaction, Virginia Tech, 2023.
\end{enumerate}

\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

% \begin{rSection}{Research}

% %------------------------------------------------

% \begin{rSubsection}{Research Assistant}{Fall 2018 - Spring 2021}{North Carolina State University (Dr. Chris Parnin)}{Raleigh, NC}
% \item Implemented and evaluated the \textit{naive telemarketer design} baseline developer recommendation approach in \textsl{tool-recommender-bot} to generate automated pull requests recommending static analysis tools to Maven projects 
% \item Mined GitHub repositories, surveyed users, and designed a user study to explore the impact of GitHub suggested changes on recommendations between developers
% \item Categorizing regular expression errors and fixes in GitHub pull requests
% \item Developed and evaluated \textsl{class-bot} systems to determining the impact of digital nudges on improving student programming behaviors 
% \end{rSubsection}
% \vspace{-5pt}
% %------------------------------------------------

% \begin{rSubsection}{Research Assistant}{Fall 2017 - Spring 2018}{North Carolina State University (Dr. Emerson-Murphy-Hill)}{Raleigh, NC}
% \item Investigated implementing a new tool recommendation approach commending developers for bug fixes, apprehending locations of similar errors, and recommending tools to help find and fix bugs
% \item Researched using crowd-sourcing to improve automatically generated Java API documentation
% \end{rSubsection}
% \vspace{-5pt}
% %------------------------------------------------

% \begin{rSubsection}{Research Assistant}{Fall 2016 - Spring 2017}{North Carolina State University (Dr. Emerson Murphy-Hill)}{Raleigh, NC}
% \item Developed and evaluated Eclipse plugin to improve code navigation for developers called \textit{Flower}
% \item Conducted a user study to determine effective characteristics of peer interactions for tool recommendations and discovered user receptiveness is the only significant attribute
% \item Published and presented this work at a peer-reviewed research conference
% \end{rSubsection}
% \vspace{-5pt}
% %------------------------------------------------

% \begin{rSubsection}{Independent Study}{Fall 2016}{North Carolina State University (Dr. Guoliang Jin)}{Raleigh, NC}
% \item Designed an algorithm using automated program repair concepts to grade introductory programming assignments
% \end{rSubsection}
% \vspace{-5pt}
% %------------------------------------------------

% \begin{rSubsection}{Computer Science Undergraduate Research Fellow}{Summer 2012 - Spring 2013}{Duke University (Dr. Susan Rodger)}{Durham, NC}
% \item Researched integrating computer science into middle school education with Alice
% \item Mapped Common Core K-12 standards to CSTA computer science education standards
% \item Created tutorials for students and teachers to create Alice worlds based on educational concepts
% \item Taught Alice programming and tutorials to K-12 teachers at summer workshops as well as middle school students during activity days
% \item Wrote senior honor's thesis \textit{``Integrating Computer Science Into Middle School Mathematics"} 
% \item Published a paper, poster, and participated in a workshop demo
% \end{rSubsection}
% \vspace{-5pt}
% %------------------------------------------------

% \begin{rSubsection}{Distributed Research Experience for Undergraduates (DREU)}{Summer 2011}{Brown University (Dr. Chad Jenkins)}{Providence, RI - Moss Beach, CA}
% \item Investigated applications for robotics in society using ROS, Python, drones, and iRobot Create robots
% \item Developed \textsl{SwagBot}, a remote controlled telepresence robot to help disabled users retrieve items
% \end{rSubsection}

% \end{rSection}
% \vspace{-10pt}


%----------------------------------------------------------------------------------------
%	PRESENTATIONS SECTION
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	FUNDING SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research Funding total = \$339,673 (\$314,173)}
\textit{I am the primary investigator (PI) unless otherwise specified. My portion is denoted in parentheses.}

\begin{enumerate}[{start=11,label=[G\arabic*]\addtocounter{enumi}{-2}}]
    \item \begin{rSubsection}{Center for Future Work Places and Practices Summer Seed Grant}{\$2,000}{Investigating the Effects of Explainable AI-Based Resume Matching on Job Seekers}{}
    \item[] June 30, 2025 -- August 31, 2025
    \end{rSubsection}
    \item \begin{rSubsection}{IEEE Diversity \& Inclusion Fund}{\$5,000}{Helping Underrepresented Students Navigate the Tech Hiring Pipeline}{}
    \item[] February 1, 2025 -- May 31, 2025
    \end{rSubsection}
    \item \begin{rSubsection}{Commonwealth Cyber Initiative (CCI): 2025 Cybersecurity Research}{\$37,500}{Bridging the Gap Between User Interface Security and CI/CD Workflows}{}   
    \item[] July 1, 2024 -- June 30, 2025
    \end{rSubsection}
    \item \begin{rSubsection}{Virginia Tech University Libraries Collaborative Research Grant}{\$10,000}{Promoting Software Engineering Best Practices for Research Software Engineers at VT}{}   
    \item Co-PI: Jonathon Bradley (\textit{University Libraries}), Virginia Tech
    \item[] July 1, 2024 -- May 1, 2025
    \end{rSubsection}
    \item \begin{rSubsection}{Sloan Foundation}{\$140,173}{Designing and Implementing Automated Solutions to Promote Software Engineering Best Practices in Research Software Development}{}
    \item[] May 1, 2024 -- October 31, 2025
    \end{rSubsection}
    \item \begin{rSubsection}{National Science Foundation CISE Career Workshop Travel Support}{\$1,500}{}{}    
    \item[] April 29-30, 2024
    \end{rSubsection}
    \item \begin{rSubsection}{CCI: Workforce and Industry Engagement Program}{\$10,000}{Understanding How Software Developers Secure User
Interfaces in Rapid Release Environments}{}
    \item[] May 1, 2024 -- August 31, 2024
    \end{rSubsection}
    \item \begin{rSubsection}{Virginia Tech Institute for Society, Culture and Environment (ISCE)}{\$7,500}{Investigating and Mitigating Bias in AI-Based Automated Resume Parsing Systems}{}
    \item[] December 1, 2023 -- June 30, 2024
    \end{rSubsection}
    \item \begin{rSubsection}{Virginia Tech Student Engineers' Council Big Contribution Grant (2023)}{\$8,000}{}{}
    \end{rSubsection}
    \item \begin{rSubsection}{CCI: Securing Interactions between Humans and Machines}{\$60,000 (\$58,500)}{Understanding the Impact of Data Privacy Regulations on Software and Its Stakeholders}{}
    \item Co-PI: Aaron Brantly (\textit{Political Science}), Virginia Tech
    \item[] December 1, 2022 -- August 31, 2024
    \end{rSubsection}
    \item \begin{rSubsection}{Google Award for Inclusion Research (2022)}{\$60,000 (\$36,000)}{Supporting Under-Resourced Software Engineering Job Seekers through Facilitating Online Collaboration in Technical Interview Preparation}{}
 \item Co-PI: Sang Won Lee (\textit{Computer Science}), Virginia Tech
 \end{rSubsection}
\end{enumerate}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TEACHING EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Teaching}
\textit{I am the instructor of record unless otherwise specified.}

%------------------------------------------------
\textbf{Virginia Tech}


CS3704: Intermediate Software Design and Engineering \\
\textsl{\small Fall 2023, Fall 2024, Fall 2025}

CS5704: Software Engineering \\
\textsl{\small Spring 2022, Spring 2023, Spring 2025}

CS6704: Advanced Topics in Software Engineering \\
\textsl{\small Spring 2024}

Independent Studies \\
\textsl{\small CS5974: Summer 2022, Spring 2023}\\
\textsl{\small CS4974: Spring 2023, Summer 2023}\\
\textsl{\small CS2974: Spring 2022}

\textbf{NC State}

\begin{tabular}{ l l }
 Summer 2020 & CSC116: Introduction to Computing - Java$^*$ \\
 Spring 2016 & CSC216: Java Programming Concepts \textit{(Teaching Assistant)} \\
 Fall 2015 & CSC326: Software Engineering \textit{(Teaching Assistant)} \\
 \footnotesize{* Virtual due to COVID-19} & \\
\end{tabular}

% \underline{\textsc{Miscellaneous}}

% \begin{rSubsection}{The Coding School}{Python Instructor}{Summer 2019}{Virtual}
% \item Tutored a high school student through the codeConnects teaching and mentorship summer program for underrepresented minorities in STEM.
% \end{rSubsection}



% %------------------------------------------------
% \begin{rSubsection}{Guest Lecture Presentation}{March 2, 2020}{North Carolina State University}{Raleigh, NC}
% \item ``Team Project Bot" lecture presentation and \texttt{class-bot} demo for \textsc{CSC326} (\textit{Software Engineering})
% \end{rSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{rSubsection}{Python Instructor}{June - August 2019}{The Coding School}{Virtual}
% \item Tutored a high school student through the codeConnects teaching and mentorship summer program for underrepresented minorities in STEM
% \end{rSubsection}
% \vspace{-5pt}
%------------------------------------------------

% \begin{rSubsection}{Alice Activity Day}{March 23, 2013}{Duke University}{Durham, NC}
% \item Taught Alice programming to local 6th grade students in two 3-hour sessions to collect data for research thesis through the Duke Computer Science Undergraduate Research Fellowship (CSURF) program
% \end{rSubsection}
% \vspace{-5pt}

%------------------------------------------------

% \begin{rSubsection}{Creating a 3D Interactive Story}{February 22, 2013}{Duke University}{Durham, NC}
% \item Taught Alice programming to 4th-6th grade girls for Females Excelling More in Math, Engineering, and Science (FEMMES) event
% \end{rSubsection}
% \vspace{-5pt}

%------------------------------------------------

% \begin{rSubsection}{Adventures in Alice}{November 30, 2012}{Oak Grove Middle School}{Winston-Salem, NC}
% \item Taught Alice programming using created tutorials to three 6th grade math and science classes
% \end{rSubsection}
% \vspace{-5pt}
%------------------------------------------------

% \begin{rSubsection}{Adventures in Alice Programming Workshops}{June 18-29 and July 9-13, 2012}{Duke University}{Durham, NC}
% \item Taught Alice programming to K-12 teachers to integrate beginner computer science concepts into K-12 curriculum
% \end{rSubsection}

\end{rSection}
% \vspace{-10pt}

%----------------------------------------------------------------------------------------
%	SERVICE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Service}

\textbf{External Service}

\textit{Grant Proposal Reviewer}
\begin{itemize}[noitemsep, topsep=0pt]
    \item CCI
    \begin{itemize}
        \item Critical Infrastructure Cybersecurity (2025)
        \item AI for Cybersecurity / Cybersecurity for AI (2024)
    \end{itemize}
    \item National Science Foundation: Secure and Trustworthy Cyberspace (SaTC) NSF panel (2024) 
\end{itemize}

\textit{Conference/Workshop Organization}

\begin{itemize}[noitemsep, topsep=0pt]
    \item International Workshop on Large Language Model-Oriented Empirical Research (LLanMER) at FSE 2025: Organizer
    \item VL/HCC 2025: Workshop Co-Chair and Grad Consortium Co-Chair
    \item FSE 2024: Web Co-Chair
\end{itemize}

\textit{Conference Session Chair}
\begin{itemize}[noitemsep, topsep=0pt]
    \item ESEM: 2025 [Program Comprehension and Review 2]
    \item FSE SEET: 2025 [Testing and Platforms]
    \item LLanMer: 2025 [LLMs for SE]
    \item VL/HCC: 2023 [Software Demonstrations]; 2025 [Creative AI \& Multimodal Interfaces]
    \item CHASE: 2022 [Mixed Session]
\end{itemize}

\textit{Program Committee Member}
\begin{itemize}[noitemsep, topsep=0pt]
    \item SANER: 2026 [Early Research Achievement Track]
    \item VL/HCC: 2025
    \item LLanMER: 2025
    \item EASE: 2025 [Short Papers and Emerging Results Track]
    \item ICSE: 2025
    \item FSE: 2023 [Tutorials Track]
    \item SIGCSE: 2023 [Birds of a Feather Track]
    \item BotSE: 2021, 2022, 2023, 2025
    \item CHASE: 2022
\end{itemize}

\textit{Conference/Workshop Reviewer}
\begin{itemize}[noitemsep, topsep=0pt]
    \item UIST: 2025
    \item CHI Late-Breaking Work: 2024
    \item CHI: 2024
    \item CSCW: 2024
\end{itemize}

\textit{Journal Reviewer}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Transactions on Software Engineering and Methodology (TOSEM): 2023, 2025
    \item IST (\textit{Regulatory Compliance in Software Engineering}): 2025
    \item Empirical Software Engineering (EMSE): 2022, 2023, 2023, 2024, 2025
    \item Communications of the ACM: 2024, 2025
    \item IEEE Software (\textit{Special Issue on Developing your Software Engineering Career}): 2023
    \item IEEE Software: 2022
    \item IEEE Software (\textit{Special Issue Bots in Software Engineering}): 2022
    \item PeerJ Computer Science: 2021
    \item TSE: 2021
\end{itemize}

\textit{Mentorship}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Code the Dream Mentor \& Reviewer: Fall 2025
\end{itemize}

\textbf{Internal Service}

\textit{Department of Computer Science}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Collegiate Faculty Search Committee: Fall 2025
    \item Virginia Tech Undergraduate Research in Computer Science (VTURCS): Fall 2025 - present
    \item Stack@CS Reading Group: Fall 2023 - present
    \item Undergraduate Program Committee: Fall 2022 - Spring 2025
    \item Software Engineering PhD Qualifying Exam Committee Chair: 2024
    \item Software Engineering PhD Qualifying Exam Committee Member: 2022, 2023, 2024
\end{itemize}

\textit{Virginia Tech}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Presidential Postdoctoral Fellowship Reviewer: 2023
    \item Future Faculty Diversity Program (2020 Cohort)
\end{itemize}

% \textit{Invited Panels}
% \begin{itemize}[noitemsep, topsep=0pt]
%     \item[] Decoding CS Grad School 2021
% \end{itemize}
% %------------------------------------------------
% \begin{subsection}{Program Committee Member}{BotSE 2021}{}{}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{}{December 1, 2020}{Panelist}{Virtual}
% \end{sSubsection}
% \vspace{-5pt}

% %------------------------------------------------
% \begin{sSubsection}{NC State CSC PhD Recruitment Weekend}{Spring 2018, 2019}{Volunteer}{Raleigh, NC}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{Bridge to the Doctorate Program}{February 15, 2019}{Graduate Student Panelist}{Raleigh, NC}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{Open Source 101}{February 2017, 2018}{Volunteer}{Raleigh, NC}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{NC-LSAMP\footnote{North Carolina Louis Stokes Alliance for Minority Participation}}{November 11, 2017}{Undergraduate Research Conference Panelist}{Raleigh, NC}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{Red Hat Diversity and Inclusion Week}{July 2017}{``Why Diversity Matters''}{Raleigh, NC}
% \end{sSubsection}
% \vspace{-5pt}

% \begin{sSubsection}{ACM Mid-Atlantic Region Programming Contest}{November 5, 2011}{Volunteer}{Durham, NC}
% \end{sSubsection}
% \vspace{-5pt}
%------------------------------------------------
\end{rSection}

\begin{rSection}{Presentations and Talks}

\textbf{Keynote Speaker}
\begin{enumerate}[{start=1,label=[K\arabic*]\addtocounter{enumi}{-2}}]
    \item \textit{International Workshop on Bots and Agents in Software Engineering} (BoatSE 2026). Workshop co-located with ICSE, April 13, 2026. Rio de Janeiro, Brazil.
\end{enumerate}

\textbf{Invited Meetings}
\begin{enumerate}[{start=2,label=[M\arabic*]\addtocounter{enumi}{-2}}]
    \item \textit{International Workshop on Benchmark Infrastructure for LLMs for Code} (BI4LLMC 2025). Invitation-only workshop co-located with FSE, June 26, 2025. Trondheim, Norway.
    \item \textit{Software Developer Diversity and Inclusion Workshop}. NII Shonan Meeting, June 26-29, 2023. Kanagawa, Japan.
\end{enumerate}

\textbf{Invited Talks}
\begin{enumerate}[{start=7,label=[T\arabic*]\addtocounter{enumi}{-2}}]
    \item \textit{What RSEs Must be Afforded: Better Software through the Right Development Practices and Tools}. Consortium for the Advancement of Scientific Software (CASS) User-Developer Experience Working Group meeting. May 6, 2025. Virtual. 
    \item \textit{Improving Software Engineering Practices and Experiences}. CCI SWVA Annual Meeting. October 16, 2024. Blacksburg, VA.
    \item CS\(|\)Source Business Meeting. September 9, 2024. Blacksburg, VA.
    \item \textit{How to Recommend Tools for Finding and Fixing Software Errors} or \textit{Overcoming the \ul{Un}wise Monkeys of Tool Adoption}. It Will Never Work in Theory (NWiT) session at Strange Loop, September 23, 2022. St. Louis, MO.
    \item \textit{Sorry to Bother You! Effective OSS Recommendations}. DevConf.US Open Source Community Conference, August 17, 2019. Boston, MA.
    \item \textit{How to Improve Software Tool Discovery and Usage}. Red Hat QECampX, October 10, 2018. Raleigh, NC.
    \item \textit{How Software Users Recommend Tools to Each Other}. Laboratory for Analytic Sciences (LAS) Wednesday Research Meeting, November 29, 2017. Raleigh, NC.
\end{enumerate}

\textbf{Invited Panels}
\begin{enumerate}[{start=3,label=[I\arabic*]\addtocounter{enumi}{-2}}]
    \item \textit{VT Academic Jobs Panel}. Virginia Tech CS Grad Council, December 2, 2021. Blacksburg, VA.
    \item \textit{NC State Career Retreat: Success Stories}. NC State Graduate School Professional Development Team, July 16, 2021. Virtual.
    \item \textit{Undergraduate Research Conference Panel}. North Carolina Louis Stokes Alliance for Minority Participation (NC-LSAMP) conference. November 11, 2017. Raleigh, NC.
\end{enumerate}

\textbf{Guest Lectures}
\begin{enumerate}[{start=1,label=[L\arabic*]\addtocounter{enumi}{-2}}]
    \item \textit{ASPT-6004: AI in History and Its Social and 
Environmental Implications}. Virginia Tech, Political Science/Alliance for Social, Political, Ethical, and Cultural Thought (ASPECT). November 12, 2025. Blacksburg, VA.
\end{enumerate}

\textbf{Miscellaneous Presentations}
\begin{enumerate}[{start=7,label=[M\arabic*]\addtocounter{enumi}{-2}}]
    \item PhD: Patiently Hoping for a Degree. \textit{Master Your Future Professional Development Workshop}. Center for the Enhancement of Engineering Diversity (CEED), Virginia Tech. September 17, 2024.
    \item \textit{New Faculty Hire Conversation w/ Chris Brown}. Office of Postdoctoral Affairs, Virginia Tech. August 9, 2023.
    \item Engineering Undergraduate Research Seminar (ENGR 1014), Virginia Tech. October 28, 2022.
    \item Faculty Research Presentation. Graduate Student Recruiting Weekend. Virginia Tech. March 18, 2022.
    \item \textit{Code World, No Blanket}. Graduate Seminar (CS 5944), Virginia Tech. September 10, 2021.
    \item Meet the Faculty. Graduate Seminar (CS 5944), Virginia Tech. September 3, 2021.
      \item \textit{Digital Nudges for Encouraging Developer Behaviors}. NC State Three Minute Thesis (3MT) competition, September 24, 2020. Virtual.  
\end{enumerate}


\end{rSection}

\begin{rSection}{Honors and Awards}
\item \textbf{CCI Research Showcase} 2025, \textit{Commonwealth Cyber Initiative}
\item \textbf{Outstanding Mentor Award} 2025, \textit{College of Engineering}
\item \textbf{Career Champion} 2023, \textit{Virginia Tech Career and Professional Development}
\item \textbf{Mentor of the Month} August 2023, \textit{Virginia Tech Graduate School}

\item \textbf{Graduate Alumni Advising Award} 2023, \textit{Virginia Tech Graduate School} {\footnotesize [\textit{nominated, did not receive}]}

\item \textbf{Best Paper Awards} VL/HCC 2023 {\footnotesize [\textit{honorable mention}]}, FSE 2022

\end{rSection}

%----------------------------------------------------------------------------------------
%	STUDENTS SECTION
%----------------------------------------------------------------------------------------
 \begin{rSection}{Advising}
 
 \textbf{PhD Students}
 %(\textit{Co-advisor}) 
 
\begin{tabular}{ l l }
 Yoseph Berhanu & Fall 2023 - present \\
 Arpit Thool & Fall 2023 - present \\
 Dibyendu Brinto Bose & Spring 2023 - present \\
 Swanand Vaishampayan & Spring 2023 - present \\
 Tianjia Wang & Spring 2023 - present \\
 Hunter Leary & Fall 2022 - present \\
 Minhyuk Ko & Fall 2022 - present \\
 Xiaoxiao Gan & Summer 2022 - present \\
 Shawal Kahlid & Spring 2022 - present
\end{tabular}
 
\textbf{MS Students}
  
  \begin{tabular}{ l l }
   Aninditaa Chauhan & Summer 2025 - present, expected Spring 2025 \\
   %\st{Jeffrey Smith & Spring 2022 - present, expected Summer 2024} \\
   %\footnotesize{* Accelerated BS/Master's program} & \\
\end{tabular} \\


 \normalsize
 \textbf{Undergraduate Students}

\begin{tabular}{ l l }
Justin Burns & Fall 2025 \\
Rishan Biju & Fall 2024-Spring 2025 \\
Dan McCabe & Fall 2024 \\
Theo Tran & Fall 2024 \\
Matthew Trimble & Spring 2024-Fall 2024 \\
Yasemin Tanyu & Fall 2023-Spring 2024 \\
\end{tabular} \\

 \normalsize
 \textbf{Graduated Students}

\begin{tabular}{ l l }
 Sahar Farzanehpour, MS & Summer 2025 \\
 James Barber & Spring 2025 \\
 Peiqing Guo, MS & Spring 2025 \\
 Swetha Rajeev & Spring 2025 \\
 Tian-Yu (Edward) Shiung & Spring 2025 \\
 Huayu Liang, MS & Fall 2024 \\
 Grace Govan, BS & Spring 2024 \\
 Md Mahim Haque, MS &  Fall 2023 \\
 Sahar Farzanehpour, BS & Spring 2023 \\
 Jenna Krebs, BS & Spring 2023 \\
 Brian Bell, BS/MS & Spring 2023 \\
 Lucas Franke, BS/MS & Spring 2023 \\
 Sean Gruber, MS & Spring 2023 \\
 Nivishree Palvannan, MS & Spring 2023 \\
 Ryan Wood, MS & Spring 2023 \\
 PeiQing Guo, BS & Spring 2022 \\

\end{tabular} \\

% \textbf{Undergraduate Summer Researchers}

% \begin{tabular}{ l l }
% \end{tabular}

\textit{Multicultural Academic Opportunities Program (MAOP)} \\
\begin{tabular}{l l}
Joaquin Tuckett & 2025 \\
 Rayn Owens (Virginia State) & 2025 \\
 Travis Chan & 2024 \\
 Baker Hasan & 2024 \\
 Javier Ralat & 2024 \\
 Omer Ahmed & 2023 \\
 Edwin Lewis II (Morehouse) & 2023 \\
 Colin Roberts & 2023 \\
 
\end{tabular} \\

 \textit{Center for the Enhancement of Engineering Diversity (CEED) Sponsored Summer Research} \\
\begin{tabular}{l l}
 Syeda Afia Hossain & 2024 \\
\end{tabular} \\

 \normalsize
\textbf{\faTrophy~Student Awards~\faTrophy}

\begin{tabular}{ l l }
 Minhyuk Ko & \textit{Aspire! Curiousity Award} \\
 Xiaoxiao Gan & \textit{2025 Outstanding Instructor of Record} \\
 Hunter Leary & \textit{Davenport Leadership Scholarship} \\
 Shawal Khalid & \textit{VL/HCC GC Travel Award} \\
 Shawal Khalid & \textit{2024 Instructor of Record} \\
 Yasemin Tanyu & \textit{VTURCS 2024}~\scriptsize{[2nd place]} \\
 Omer Ahmed & \textit{2024 LSAMP VA---NC Alliance Undergraduate Research Symposium}~\scriptsize{[1st place]}\\
 Omer Ahmed & \textit{Dr. Wayne Scales Undergraduate Research and Creative Scholarship} \\
  & \textit{Symposium} \scriptsize{[2nd place]}\\
 Minhyuk Ko & \textit{VL/HCC Best Short Paper Honorable Mention} \\
 Shawal Khalid & \textit{Bitshares Fellowship} \\
 Brian Bell & \textit{New Horizon Graduate Scholar} \\
\end{tabular} \\

  \textbf{Thesis Advisory Committees} \\
  (\textit{Student advisor is in italics with graduation year in parentheses.})
 \begin{itemize}[noitemsep]
    \item Francis Obeng, PhD (\textit{Dr. Eli Tilevich})
    \item Sean Chambers, PhD (\textit{Chris Campo-Bowen})
    \item Tri Pham, PhD (\textit{Dr. Caitlin Kelleher})  [Washington University in St. Louis]
    \item Leo St. Amour, PhD (\textit{Dr. Eli Tilevich})
    \item Yeana Bond, PhD (\textit{Dr. Na Meng})
    \item Tien Nguyen, PhD (\textit{Dr. Muhammad Ali Gulzar})
    \item Alex Hicks, PhD (\textit{Dr. Cliff Shaffer})
    \item Taufiq Daryanto, PhD (\textit{Dr. Eugenia Rho})
    \item Sabaat Haroon, PhD (\textit{Dr. Muhammad Ali Gulzar})
    \item Provakar Mondal, PhD (\textit{Dr. Eli Tilevich)}
    \item Md Mahir Asef Kabir, PhD (\textit{Dr. Na Meng}) \\
    ------------------------------------------------------------------
    \item Gayatri Bhatambarekar, MS (\textit{Dr. Na Meng} and \textit{Dr. Abhijit Sarkar}, 2025)
    \item Ananya Prakash, MS (\textit{Dr. Mohammed Seyam}, 2025)
    \item Rishith Gandham, MS (\textit{Dr. Na Meng}, 2024)
    \item Miles Frantz, PhD (\textit{Dr. Daphne Yao}, 2024)
    \item Ashwin Rachha, MS (\textit{Dr. Mohammed Seyam}, 2024)
    \item Yi Lu, MS (\textit{Dr. Sang Won Lee}, 2024)
    \item Divyansh Mishra, MS (\textit{Dr. Steve Edwards}, 2023)
    \item Ming Zhu, PhD (\textit{Dr. Ismini Lourentzou} and \textit{Dr. Daphne Yao}, 2023)
    \item Juntong Chen, MS (\textit{Dr. Na Meng}, 2022)
 \end{itemize}
 \footnotesize{* All students are in the Department of Computer Science at Virginia Tech unless otherwise specified}

\end{rSection}

% %------------------------------------------------
% \begin{sSubsection}{Future Faculty Diversity Program at Virginia Tech$^*$}{October 4-7, 2020}{}{Virtual}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{Red Hat Research Day \textit{Infrastructure Software}}{September 30, 2020}{}{Virtual}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{NC State Academic Packways$^*$}{June 4-5, 2020}{}{Virtual}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{NC State Virtual Writing Retreat$^*$}{May 4-8, 2020}{}{Virtual}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{Open Source 101 at Home$^*$}{May 12, 2020}{}{Virtual}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{All Things Open}{October 2016, 2017, 2018, 2019, 2020}{Red Hat}{Raleigh, NC}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{URMD Grad Cohort Workshop}{March 21-23, 2019}{CRA}{Waikoloa Village, HI}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{ESEC/FSE 2018}{November 5-9, 2018}{ACM}{Lake Buena Vista, FL}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{NSBC 2018}{August 9-11, 2018}{National Society of Blacks in Computing}{New Orleans, LA}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{Open Source 101}{February 2017, 2018}{Opensource.com}{Raleigh, NC}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{NSBC 2017}{June 1-3, 2017}{National Society of Blacks in Computing}{Atlanta, GA}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}{ESEC/FSE 2016}{November 14-18, 2016}{ACM}{Seattle, WA}
% \end{sSubsection}
% \vspace{-5pt}
% %------------------------------------------------
% \begin{sSubsection}
% {LeaderShape}{August 2012}{Duke University}{Sophia, NC}
% \end{sSubsection}
% \vspace{-5pt}
% \end{rSection}
%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
% \begin{rSection}{Honors and Awards}

% \begin{sSubsection}
% {DevConf.US Diversity Travel Scholarship}{June 25, 2019}{Red Hat}{Boston, MA}
% \end{sSubsection}
% \vspace{-5pt}

% \begin{sSubsection}
% {SIGSOFT CAPS NSF Travel Award}{March 27, 2019}{NSF}{(ICSE 2019) Montreal, QC, Canada}
% \end{sSubsection}
% \vspace{-5pt}

% \begin{sSubsection}
% {Graduate Merit Award}{August 2015}{North Carolina State University}{Raleigh, NC}
% \end{sSubsection}
% \vspace{-5pt}

% \begin{sSubsection}
% {Goldman Sachs Research Scholar}{Summer 2012}{Goldman Sachs}{Durham, NC}
% \end{sSubsection}
% \vspace{-5pt}

% \begin{sSubsection}
% {Undergraduate Research Fellowship}{May 2012 - May 2013}{Duke University}{Durham, NC}
% \end{sSubsection}
% \vspace{-5pt}

% \begin{sSubsection}
% {Computing Research Association DREU}{Summer 2011}{Brown University}{Providence, RI}
% \end{sSubsection}
% \vspace{-5pt}

% \end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
